SMT-Boosted Security Types for Low-Level MPC

### 2025-11-14 toplas26/examples.tex
checkpoint

@@

\input{bdoz}

@@

%%%%%%%%%%%%%%%%%%
%%% ARCHIVAL BELOW
%%%%%%%%%%%%%%%%%%
\begin{comment}
\begin{verbatimtab}
andtableygc(g,x,y)
{
   let table = (~r[g],~r[g],~r[g],r[g])
   in permute4(r[x],r[y],table)
}

m[x]@1 := s2(s[x],r[x],~r[x])@2;
m[x]@1 as s[x]@2 xor r[x]@2;

// m[x]@1 : { c(r[x]@2, { s[x]@2 }) }

m[y]@1 := OT(s[y]@1,r[y],~r[y])@2;
m[y]@1 as s[y]@1 xor r[y]@2;

// m[y]@1 : { c(r[y]@2, { s[y]@1 }) }

m[ag]@1 := OT4(m[x]@1, m[y]@1, andtable(ag,r[x],r[y]))@2;
m[ag]@1 as  ~((r[x]@2 = m[x]@1) and (r[y]@2 = m[y]@1)) xor r[ag]@2;

// m[ag]@1 : { c(r[ag]@2, {r[x]@2, r[y]@2, m[x]@1,  m[y]@1} }

p[o] := OT2(m[ag]@1, perm2(r[ag],(false,true)))@2

// p[o] : { c(r[ag]@2, {r[x]@2, r[y]@2,  m[x]@1,  m[y]@1}), r[ag]@2  }

out@1 := p[o]@1

// out@1 == s[x] and s[y]
\end{verbatimtab}

\begin{verbatimtab}
    encodegmw(in, i1, i2) {
      m[in]@i2 := (s[in] xor r[in])@i1;
      m[in]@i1 := r[in]@i1
    }

    andtablegmw(x, y, z) {
      let r11 = r[z] xor (m[x] xor true) and (m[y] xor true) in
      let r10 = r[z] xor (m[x] xor true) and (m[y] xor false) in
      let r01 = r[z] xor (m[x] xor false) and (m[y] xor true) in
      let r00 = r[z] xor (m[x] xor false) and (m[y] xor false) in
      { row1 = r11; row2 = r10; row3 = r01; row4 = r00 }
    }

    andgmw(z, x, y) {
      let table = andtablegmw(x,y,z) in
      m[z]@2 := OT4(m[x],m[y],table,2,1);
      m[z]@2 as ~((m[x]@1 xor m[x]@2) and (m[y]@1 xor m[y]@2)) xor r[z]@1);
      m[z]@1 := r[z]@1
    }

    // and gate correctness postcondition
    {} andgmw { m[z]@1 xor m[z]@2 == (m[x]@1 xor m[x]@2) and (m[y]@1 xor m[y]@2) }

    // and gate type
    andgmw :
     Pi z,x,y .
     {}
     { { r[z]@1 },
       (m[z]@1 : { r[z]@1 }; m[z]@2 : {c(r[z]@1, { m[x]@1, m[x]@2, m[y]@1, m[y]@2 })} ),
       m[z]@1 xor m[z]@2 == (m[x]@1 xor m[x]@2) and (m[y]@1 xor m[y]@2)}

    xorgmw(z, x, y) {
      m[z]@1 := (m[x] xor m[y])@1; m[z]@2 := (m[x] xor m[y])@2;
    }

    decodegmw(z) {
      p["1"] := m[z]@1; p["2"] := m[z]@2;
      out@1 := (p["1"] xor p["2"])@1;
      out@2 := (p["1"] xor p["2"])@2
    }

    prot() {
      encodegmw("x",2,1);
      encodegmw("y",2,1);
      encodegmw("z",1,2);
      andgmw("g1","x","z");
      xorgmw("g2","g1","y");
      decodegmw("g2")
    }

    {} prot { out@1 == (s["x"]@1 and s["z"]@2) xor s["y"]@1 }
\end{verbatimtab}

\begin{verbatimtab}
  secopen(w1,w2,w3,i1,i2) {
      pre(m[w1++"m"]@i2 == m[w1++"k"]@i1 + (m["delta"]@i1 * m[w1++"s"]@i2 /\
          m[w1++"m"]@i2 == m[w1++"k"]@i1 + (m["delta"]@i1 * m[w1++"s"]@i2));
      let locsum =  macsum(macshare(w1), macshare(w2)) in
      m[w3++"s"]@i1 := (locsum.share)@i2;
      m[w3++"m"]@i1 := (locsum.mac)@i2;
      auth(m[w3++"s"],m[w3++"m"],mack(w1) + mack(w2),i1);
      m[w3]@i1 := (m[w3++"s"] + (locsum.share))@i1
  }

  _open(x,i1,i2){
    m[x++"exts"]@i1 := m[x++"s"]@i2;
    m[x++"extm"]@i1 := m[x++"m"]@i2;
    assert(m[x++"extm"] == m[x++"k"] + (m["delta"] * m[x++"exts"]));
    m[x]@i1 := (m[x++"exts"] + m[x++"s"])@i2
  }`

  _sum(z, x, y,i1,i2) {
      pre(m[x++"m"]@i2 == m[x++"k"]@i1 + (m["delta"]@i1 * m[x++"s"]@i2 /\
          m[y++"m"]@i2 == m[y++"k"]@i1 + (m["delta"]@i1 * m[y++"s"]@i2));
      m[z++"s"]@i2 := (m[x++"s"] + m[y++"s"])@i2;
      m[z++"m"]@i2 := (m[x++"m"] + m[y++"m"])@i2;
      m[z++"k"]@i1 := (m[x++"k"] + m[y++"k"])@i1;
      post(m[z++"m"]@i2 == m[z++"k"]@i1 + (m["delta"]@i1 * m[z++"s"]@i2)
  }

  sum(z,x,y) { _sum(z,x,y,1,2);_sum(z,x,y,2,1) }

  open(x) { _open(x,1,2); _open(x,2,1) }

  sum("a","x","d");
  open("d");
  sum("b","y","e");
  open("e");
  let xys =
      macsum(macctimes(macshare("b"), m["d"]),
             macsum(macctimes(macshare("a"), m["e"]),
                    macshare("c")))
  let xyk = mack("b") * m["d"] + mack("a") * m["e"] + mack("c")

  secopen("a","x","d",1,2);
    secopen("a","x","d",2,1);
    secopen("b","y","e",1,2);
    secopen("b","y","e",2,1);
    let xys =
      macsum(macctimes(macshare("b"), m["d"]),
             macsum(macctimes(macshare("a"), m["e"]),
                    macshare("c")))
    in
    let xyk = mack("b") * m["d"] + mack("d") * m["d"] + mack("c")               
    in
    secreveal(xys,xyk,"1",1,2);
    secreveal(maccsum(xys,m["d"] * m["e"]),
              xyk - m["d"] * m["e"],
              "2",2,1);
    out@1 := (p[1] + p[2])@1;
    out@2 := (p[1] + p[2])@2;
\end{verbatimtab}

\end{comment}

>>>>

\begin{fpfig}[t]{2-party gate library with Beaver Triple multiplication, circuit definition, and compositional correctness conditions.}{fig-beaver}
\footnotesize
\begin{verbatimtab}
IDEALF() { (s["x"]@1 + s["y"]@2) + (s["i"]@1 * s["j"]@2) }

RECON(x) { (m[x]@1 + m[x]@2) }

BEAVERTRIP(x) {
  m[x++"c"]@3 == r[x++"a"]@3 * r[x++"b"]@3 AND
  m[x++"a"]@1 + m[x++"a"]@2 == r[x++"a"]@3 AND
  m[x++"b"]@1 + m[x++"b"]@2 == r[x++"b"]@3 AND
  m[x++"c"]@1 + m[x++"c"]@2 == m[x++"c"]@3 
}

sshare(x:string, i1:cid, i2:cid) { m[x]@i2 := (s[x] + -r[x])@i1; m[x]@i1 := r[x]@i1 }

_open(x:string, i1:cid, i2:cid, n:string){ p[x++"n"] := m[x]@i2; m[x++"p"]@i1 = p[x++"n"] + m[x]@i1 }

open(x:string) { _open(x,1,2,"1"); _open(x,2,1,"2") }

secopen(d:string;x:string,a:string) { sum(d, x, a); open(d) }

_sum(z:string, x:string, y:string, i:cid) { m[z]@i := (m[x] + m[y])@i }

sum(z:string, x:string, y:string){ _sum(z,x,y,1); _sum(z,x,y,2) }
postcondition: ( RECON(z) == RECON(x) + RECON(y) )

_mult(z : string, y : string, i : cid) {
    m[z]@i := (m[z++"d"] * m[y] + -m[z++"e"] * m[z++"a"] + m[z++"c"])@i
}

precondition: ( BEAVERTRIP(z) )
mult(z : string, x : string, y : string) {
  secopen(z++"d", x, z++"a"); secopen(z++"e", y, z++"b"); _mult(z,y,1); _mult(z,y,2)
}
postcondition: ( RECON(z) == RECON(x) * RECON(y) )

precondition: ( BEAVERTRIP("k") ) 
main() {
    sshare("x", 1, 2); sshare("y", 2, 1); sshare("i", 1, 2); sshare("j", 2, 1);
    sum("z","x","y"); mult("k","i","j"); sum("out","z","k");
    open("out")
}
postcondition: ( m["out"]@1 == IDEALF() )
\end{verbatimtab}
\end{fpfig}

\begin{fpfig}[t]{2-party gate library with Beaver Triple multiplication extended with share type annotations.}{fig-beaver-types}
\footnotesize
\begin{verbatimtab}
sshare(x:string, i1:cid, i2:cid) {
   m[x++"s"]@i1 := (s[x] + -r[x])@i2; m[x++"s"]@i2 := r[x]@i2;
   [m[x++"s"]@i1,m[x++"s"]@i2] : shares
}

([m[x]@i1, m[x]@i2] : shares)
open(x:string) {
  _open(x,1,2,"1"); _open(x,2,1,"2");
  [p[x++"1"],p[x++"2"]] : shares;
  m[d++"p"]@2 as m[d++"p"]@1  
}

precondition: ([m[x]@i1, m[x]@i2] : shares,
	       [m[a]@i1, m[a]@i2] : shares)
secopen(d:string;x:string,a:string) {
    sum(d, x, a); open(d);
    m[d++"p"]@1 as RECON(x) + r[x++a]@o;
    <m[d++"p"]@1> : public;
    <m[d++"p"]@2> : public
}

precondition: ([m[x]@1,m[x]@2] : shares;
               [m[y]@1,m[y]@2] : shares)
sum(z:string, x:string, y:string) {
    _sum(z,x,y,1); _sum(z,x,y,2);
    [m[z]@1,m[z]@2] : shares
}
postcondition: ( RECON(z) == RECON(x) + RECON(y) )

precondition: ( [m[x]@1,m[x]@2] : shares;
                [m[y]@1,m[y]@2] : shares;
	        [m[x++"c"]@1,m[x++"c"]@2] : shares ),
	       ( BEAVERTRIP(z) )
mult(z : string, x : string, y : string) {
    secopen(z++"d", x, z++"a"); secopen(z++"e", y, z++"b"); _mult(z,y,1); _mult(z,y,2);
    [m[z]@i1,m[z]@i2] : shares
}
postcondition: ( RECON(z) == RECON(x) * RECON(y)) )
\end{verbatimtab}
\end{fpfig}

\begin{fpfig}[t]{2-party gate library with Beaver Triple multiplication extended with BDOZ MACs.}{fig-beaver-bdoz}
\footnotesize
\begin{verbatimtab}
MACOK(x, i1, i2) { m[x++"m"]@i2 == m[x++"k"]@i1 + (m["delta"]@i1 * m[x++"s"]@i2) }

MACed(x) { MACOK(x, 1, 2) AND MACOK(x, 2, 1) }

_open(x:string, i1:cid, i2:cid, n:string){
    p[x++"sn"] := m[x++"s"]@i2;
    p[x++"mn"] := m[x++"m"]@i2;
    assert(p[x++"mn"] = m[x++"k"] + (m["delta"] * p[x++"sn"]))@i1;
    m[x++"p"]@i1 = p[x++"sn"] + m[x]@i1
}

precondition: ( MACed(x) )
open(x:string) { _open(x,1,2,"1"); _open(x,2,1,"2") }

_sum(z:string, x:string, y:string, i:cid){
    m[z++"s"]@i := (m[x++"s"] + m[y++"s"])@i;
    m[z++"m"]@i := (m[x++"m"] + m[y++"m"])@i;
    m[z++"k"]@i := (m[x++"k"] + m[y++"k"])@i
}

precondition: ( MACed(x) AND MACed(y) )
sum(z:string, x:string, y:string){ _sum(z,x,y,1); _sum(z,x,y,2) }
postcondition: ( MACed(z) AND RECON(z) == RECON(x) + RECON(y) )

_mult(z : string, y : string, i : cid) {
   m[z++"s"]@i := (m[z++"d"] * m[y++"s"] + -m[z++"e"] * m[z++"as"] + m[z++"cs"])@i;
   m[z++"m"]@i := (m[z++"d"] * m[y++"m"] + -m[z++"e"] * m[z++"am"] + m[z++"cm"])@i;
   m[z++"k"]@i := (m[z++"d"] * m[y++"k"] + -m[z++"e"] * m[z++"ak"] + m[z++"ck"])@i
}

precondition: ( MACed(x) AND MACed(y) AND
                MACed(z++"a") AND MACed(z++"b") AND MACed(z++"c") AND BEAVERTRIP(z) )
mult(z : string, x : string, y : string) {
    secopen(z++"d", x, z++"a"); secopen(z++"e", y, z++"b"); _mult(z,y,1); _mult(z,y,2);
}
postcondition: ( RECON(z) == RECON(x) * RECON(y) )

\end{verbatimtab}
\end{fpfig}

@@

% \input{bdoz}

@@
